### 2021-05-18 README.Rmd

[![](https://img.shields.io/badge/devel%20version-0.0.1.600-blue.svg)](https://codecov.io/gh/c1au6i0/covid19census?branch=master)
[![Build Status](https://travis-ci.com/c1au6i0/covid19census.svg?branch=master)](https://travis-ci.com/c1au6i0/covid19census)
[![Codecov test coverage](https://codecov.io/gh/c1au6i0/covid19census/branch/master/graph/badge.svg)](https://codecov.io/gh/c1au6i0/covid19census?branch=master)

@@

* `us_acm_househ`: several metric regarding household composition, including poverty, education, ancestry (2018).
* `us_age_sex`: age and sex distribution (2018).
* `us_fl65`:  percentage of fee-for-service (FFS) Medicare enrollees that had an annual flu vaccination (2017)
* `us_hospbeds`: total hospital beds in each county (2019).
* `us_netinc`: median househould income (2018).
* `us_mmd`: data of 2017 regarding the  prevalence found in medicare beneficiaries of 
    * many medical and chronic conditions (Alzheimer, chronic kidney, obesity, depression, obstructive pulmonary, disease, arthritis, diabetes, osteoporosis, asthma, atrial  fibrillation, ischemic hearth, myocardial infarction, hypertension).
    * several type of cancer.
    * emergency,  medical admissions and annual visits.
    * pneumoccocal vaccine.
    * tobacco use.
* `us_pm2.5`: Emissions of pm2.5 in micro g/m3
* `us_race`: estimated races in population (2018).

>>>>

[![](https://img.shields.io/badge/version-0.1.0-blue.svg)](https://codecov.io/gh/c1au6i0/covid19census?branch=master)
[![Build Status](https://travis-ci.com/c1au6i0/covid19census.svg?branch=master)](https://travis-ci.com/c1au6i0/covid19census)
[![Codecov test coverage](https://codecov.io/gh/c1au6i0/covid19census/branch/master/graph/badge.svg)](https://codecov.io/gh/c1au6i0/covid19census?branch=master)

@@

* `us_acm_househ`: several metric regarding household composition, including poverty, education, ancestry (2018).
* `us_age_sex`: age and sex distribution (2018).
* `us_fl65`:  percentage of fee-for-service (FFS) Medicare enrollees that had an annual flu vaccination (2019)
* `us_hospbeds`: total hospital beds in each county (2019).
* `us_netinc`: median househould income (2018).
* `us_mmd`: data of 2019 regarding the  prevalence found in medicare beneficiaries of 
    * many medical and chronic conditions (Alzheimer, chronic kidney, obesity, depression, obstructive pulmonary, disease, arthritis, diabetes, osteoporosis, asthma, atrial  fibrillation, ischemic hearth, myocardial infarction, hypertension).
    * several type of cancer.
    * emergency,  medical admissions and annual visits.
    * pneumoccocal vaccine.
    * tobacco use.
* `us_pm2.5`: Emissions of pm2.5 in micro g/m3
* `us_race`: estimated races in population (2018).
